Timely Object Recognition

### 2012-05-30 writeups/nips12/evaluation.tex
working on writeup
reworked paper quite a bit, but not done

>>>>

\todo{completely rework when settled on results story}

One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.

We use one-vs-all deformable part-model classifiers on a HOG featurization of the image \cite{Felzenszwalb2010a}, with associated linear classification of the detections.

### 2012-05-30 writeups/nips12/related.tex
reworked paper quite a bit, but not done

@@

\paragraph{Contect}
Context of course has a long history in vision.
One source of context is the scene or non-detector cues; for the PASCAL VOC, these are quantitatively considered in~\cite{Divvala2009}. 
Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}. These  statistics interlink individual object detection tasks as well as image classification. Exploiting this information has shown to improve classification as well as detection tasks (e.g. \cite{Torralba, visual phrases}).
A critical summary of the main approaches to using context for object detection is given in \cite{Galleguillos2010}.

>>>>

Multi-class performance is evaluated by averaging the individual per-class AP values.
Since our use case is motivated by a potential advertising system, we generalize this metric to a weighted average, with the weights set by the \emph{values} of the classes.

@@

\paragraph{Context}
Context of course has a long history in vision.
One source of context is the scene or non-detector cues; for the PASCAL VOC, these are quantitatively considered in~\cite{Divvala2009}. 
Another source is inter-object context, used for detection in a random field setting in~\cite{Torralba2004}. These  statistics interlink individual object detection tasks as well as image classification. Exploiting this information has shown to improve classification as well as detection tasks (e.g. \cite{Torralba, visual phrases}).
A critical summary of the main approaches to using context for object detection is given in \cite{Galleguillos2010}.

### 2012-05-30 writeups/nips12/technical.tex
reworked paper quite a bit, but not done

Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results $\emph{detect}(I)$ by running detector and other \emph{actions} sequentially.

The policy repeatedly selects an action $a_i$ from a set of actions $\mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
The set of actions can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.

@@

\subsubsection{Sequential Execution}
An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
The common classifier cascade \cite{Viola2001} is an example.
In contrast, our goal is to learn a dynamic, or ``closed-loop,'' policy, which would exploit the signal in inter-object and scene context for a maximally efficient path through the actions.

An action $a_i$ that consists of running a classifier $L_i$ returns a real-valued observation $o_i \sim P(O_i)$.
The state records the fact that $a$ has been taken by adding it to the initially empty set $\mathcal{O}$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | L_i \in \mathcal{O}\}$.

We define the belief state $b$ of the decision process by the the distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$.
Additionally, $b$ records the time into episode $t$, and the set of executed actions $\mathcal{O}$ with corresponding observations $\mathbf{o}$.

A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial belief state $b^0$ and action $a^0$ to the next pair $b^1$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

The policy's performance at time $t$ is determined by the detection and classification observations that have been observed at the last belief state $b^j$ before that point.
For classification of unobserved classes, we treat the corresponding values of $P(\mathbf{C})$ as the set of confidence scores $\{\emph{classify}(k)\}$.
Detection results of unobserved classes are an empty set.

Our notation is summarized in \autoref{tab:notation}.

@@

\section{Selecting actions} \label{sec:value}
\comment{Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).}
As our goal is to pick actions dynamically, we want to formulate a function $V(b,a)$  that assigns a value to a potential action, given the current state of the decision process.
We can then define the policy as simply the untaken action with the maximum value:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
\end{align}

For this policy to be \emph{closed-loop}, the observations $o_i$ generated by taking an action $a_i$ need to update $b$ and thus influence the selection of the next action.
Figure~\ref{fig:pomdp} visualizes such an execution process.

One simple heuristic value function that we can try is simply picking the action corresponding to the class presence variable $C_k$ with the highest probability.
Of course, we'd like to learn the value function from the data, but the above heuristic will be used as a baseline in the evaluation to follow.

Before we discuss how to set $V(b,a_i)$ such that our policy obtains best performance under our evaluation, we present our model for updating the belief state with observations.

\subsection{The model of the belief state}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
\caption{
The MRF inference model used in our system.
We show a point in the middle of the decision process for 3 classes; one action has already been taken.
\comment{Some classifiers have already been observed.}
}
\label{fig:model}
\end{figure}

 \todo{section on a ``fast approximation'' to this based on the n-gram counts we had before?}

\subsection{Learning the Value Function}

Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
We can formulate such a policy as a scalar product:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a_i)
\end{align}
where $\phi(b,a_i)$ is a feature vector representation of the belief state.
This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.

This representation allows us to use a single vector of weights $\theta$ as a compact representation of our policy.

At each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
The final evaluation metric is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, with $J$ being the last step of the process with $t \le T_d$.

Ideally, the value function for a point in the decision process $b^j$ should give the expected value of the final evaluation metric, over all possible histories starting at point $j$:
\begin{align}
V(b^j,a_i) = \mathbb{E}_{h^j \sim P(h^j|b,a_i)}[R(h^j)]
\end{align}

@@

We formulate two reward definitions: one strives to match the final AP evaluation of the detections, and one is motivated by lowering uncertainty of $P(\mathbf{C})$.

@@

\subsubsection{Reward: decrease in mean entropy}
We also consider a similar additive reward function based on the mean entropy of the variables $P(C_k)$: $\frac{1}{K}\sum_{k=1}^K H(C_k)$, where $H(C_k) = - \sum_{c_k \in {0,1}} P(c_k) \log P(c_k)$.
We follow the same setup as above, but strive to maximize the area \emph{above} the curve of mean entropy vs. time.

The goal of a policy that maximizes these rewards is to take actions that reduce uncertainty of the most uncertain variables most quickly.

\subsection{Learning the weights}

@@

>>>>

Our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs a list of multi-class detection results by running detector and other \emph{actions} sequentially.

The policy repeatedly selects an action $a_i \in \mathcal{A}$, executes it, receiving observations $o_i$, and then selects the next action.
The set of actions $\mathcal{A}$ can include both classifiers and detectors: anything that would be useful for inferring the contents of the image.

@@

\subsection{Sequential Execution}
An ``open-loop'' policy takes actions in a sequence that does not depend on observations received from previous actions.
The common classifier cascade \cite{Viola2001} is an example.
In contrast, our goal is to learn a dynamic, or ``closed-loop,'' policy, which would exploit the signal in inter-object and scene context for a maximally efficient path through the actions.

The basis for the decisions made by the decision process is called the \emph{state}.
The state, $b$, includes the currently believed distribution over class presence variables $P(\mathbf{C}) = P(C_1, \dots, C_K)$, where we write $P(C_k)$ to mean $P(C_k=1)$

Additionally, the state records the fact that an action $a_i$ has been taken by adding it to the initially empty set $\mathcal{O}$ and recording the resulting observations $o_i$.
We refer to the current set of observations as $\mathbf{o} = \{o_i | a_i \in \mathcal{O}\}$.
The state also includes the time into episode $t$, and the setup and deadline times $T_s,T_d$.

A recognition \emph{episode} takes an image $\mathcal{I}$ and proceeds from the initial state $b^0$ and action $a^0$ to the next pair $(b^1,a^1)$, and so on until $t$ exceeds $T_d$.
At that point, the policy is terminated and a new episode begins on a new image.

The policy's performance at time $t$ is determined by the detections that are part of the set of observations $\mathbf{o}$ at the last state $b^j$ before $t$.
Detection results of unobserved classes are an empty set.

@@

\subsection{Selecting actions based on expected reward} \label{sec:value}
As our goal is to pick actions dynamically, we want a function $V(b,a): B \times \mathcal{A} \mapsto \mathbb{R}$, where $B$ is the space of all possible states, to assign a value to a potential action, given the current state of the decision process.
We can then define the desired policy $\pi$ as simply taking the (untaken) action with the maximum value:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} V(b,a_i)
\end{align}

This formulation can represent a closed-loop policy if the observations $\mathbf{o}$ (part of the state $b$) play a role in determining the value of a potential action.

Before proceeding, we note that that although the action space $\mathcal{A}$ is quite manageable, consisting of the detectors and classifier we would like to run on the image, the space of possible states $B$ is infinite.
Therefore we cannot learn a tabular representation of $V(b,a)$, and so use function approximation to represent it \cite{Sutton1998}.
We featurize the state-action pair and assume linear structure: $V^\pi(b,a) = \theta_\pi^\top  \phi(b,a_i)$.

Rembmer that at each time step, our system is evaluated by properties of the state $b$ (the list of detections and the classification outputs).
The final evaluation metric is a function of the history of execution $h^0=b^0,b^1,\dots,b^J$, with $J$ being the last step of the process with $t \le T_d$.

\todo{rework the below from the persepctive of individual action rewards, not reward of whole history}
Ideally, the value function for a point in the decision process $b^j$ should give the expected value of the final evaluation metric, over all possible histories starting at point $j$:
\begin{align}
V(b^j,a_i) = \mathbb{E}_{h^j \sim P(h^j|b,a_i)}[R(h^j)]
\end{align}

@@

@@

\todo{discuss the raw vs. the normalized area, saying we'll try both}

\subsection{Feature representation and learning the policy}
\todo{write out current approach}

@@

\subsection{Updating probabilities}
\begin{figure}[h!]
\centering
\includegraphics[width=0.56\linewidth]{../figures/inf_model_mrf_1.pdf}
\caption{
The MRF inference model used in our system.
We show a point in the middle of the decision process for 3 classes; one action has already been taken.
\comment{Some classifiers have already been observed.}
}
\label{fig:model}
\end{figure}

\todo{Rework from the persepctive of two potential ways of updating the beliefs with observations: just putting them in directly vs. going through MRF. De-emphasize the need for the model, treat it as an extra oomph.}
